Community-Conditioned Language Models

### 2021-06-10 paper/paper.tex
oops, unicode
move pcas to main; use same axis limits

\usepackage{newunicodechar}

\usepackage{pgfplots}
\usepgfplotslibrary{groupplots}
\usepgfplotslibrary{statistics}
\pgfplotsset{compat=1.16}
\pgfplotsset{every tick label/.append style={font=\footnotesize}}

@@

Thus if \(d(L,S)\) is below the mean by several standard deviations, we can safely
assume that there is statistically significant correlation between
\(L\) and \(S\).  This is the case: we observe a difference between 61 and 68 standard deviations
(\cref{tab:embedding-correlations}). Further, it is clear that the CCLM embeddings
capture some of the same information as the social-network embeddings.
We also give a sense of \emph{how} the correlation is manifested by
analysis of the two principal components of correlation in the
linguistic embeddings, \(U_0\) and \(U_1\). To do so we plot the
projection of each embedding along their first two principle components
which, together with the corresponding singular values, gives an idea
of how much and in what way they differ (see supplementary materials).

>>>>

\usepackage{newunicodechar}
\input{unicode_symb}
\usepackage{pgfplots}
\usetikzlibrary{arrows}
\usepgfplotslibrary{groupplots}
\usepgfplotslibrary{statistics}
\pgfplotsset{compat=1.16}
\pgfplotsset{every tick label/.append style={font=\tiny}}

@@

Thus if \(d(L,S)\) is below the mean by several standard deviations, we can safely
assume that there is statistically significant correlation between
\(L\) and \(S\).  This is the case: we observe a difference between 61 and 68 standard deviations
(\cref{tab:embedding-correlations}). Further, it is clear that the CCLM embeddings
capture some of the same information as the social-network embeddings.
We also give a sense of \emph{how} the correlation is manifested by
analysis of the two principal components of correlation in the
linguistic embeddings, \(U_0\) and \(U_1\). To do so we plot the
projection of each embedding along their first two principle components
which, together with the corresponding singular values, gives an idea
of how much and in what way they differ (see~\cref{fig:pca-aligned}).

\begin{figure*}[t]
    \centering
  \begin{tikzpicture}
    \begin{groupplot}[%
      group style={
        group size=2 by 1,
        horizontal sep=0pt,
      },
      xmin=-1, xmax=1,
      ymin=-1, ymax=1,
      xtick={-0.5,0.5}, ytick={-0.5,0.5},
      axis x line=middle,
      axis y line=middle,
      axis line style={(-)},
      axis on top=true,
      width=0.55\textwidth,
      height=0.55\textwidth,
      scatter/classes={
        0={mark=x, blue},
        1={mark=+, orange},
        2={mark=o, green},
        3={mark=triangle, gray},
        4={mark=star, magenta},
        5={mark=diamond, red}
      },
      ]
      \nextgroupplot[
        %xlabel=$U_0$, ylabel=$U_1$,
        legend cell align=left,
        legend style={font=\tiny},
        legend entries = {
          offmychest confession relationships relationship\_advice SuicideWatch, 
          TrueReddit China europe nyc socialism,
          frugalmalefashion running MechanicAdvice personalfinance Flipping,
          darksouls skyrimmods dragonage Xcom MonsterHunter,
          amiugly Rateme ladybonersgw SchoolIdolFestival GoneWildPlus,
          facepalm CrappyDesign mildlyinfuriating cringepics oddlysatisfying,
        },
        %legend pos=outer south east
        legend to name=pcalegend
      ]
      \addplot[%
        scatter, only marks,
        mark options={thick, scale=0.75},
       scatter src=explicit symbolic,
        ] table [x={web-PCA0}, y={web-PCA1}, meta={web-cluster}] {floats/comm.csv};
      \nextgroupplot[
      %xlabel=$V_0$, ylabel=$V_0$
      ]
      \addplot[%
        scatter, only marks,
        mark options={thick, scale=0.75},
       scatter src=explicit symbolic,
        ] table [x={lstm-3-1-PCA0}, y={lstm-3-1-PCA1}, meta={web-cluster}] {floats/comm.csv};
    \end{groupplot}
  \end{tikzpicture}
  \captionof{figure}{First two components of the aligned social (top) and linguistic (bottom) embeddings,
    where the lingusitic embedding is taken from the LTSM with $l_c=1$.
    Correlation between these directions is given by $\sigma_0 = 53.4$ and $\sigma_1 = 35.6$.
    Colors are assigned by k-means clustering of the social embedding. The legend shows the
    closest 5 communites to each cluster centroid.}
  \label{fig:pca-aligned}
\end{figure*}
